---
title: "Assignment 3"
author: "Nicole Jimenez"
date: "5/29/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load libraries
```{r  include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(forcats)
library(RColorBrewer)
library(knitr)
```

## Load Data 
```{r}
load("~/Google Drive/EdD/term_5/data science/scripts_data_files/attrition.Rdata")
```

#Use the attrition dataset to answer the following questions. As always, your assignment must be turned in as a .Rmd file.

#Create a graph that shows the distribution of monthly income. I decided income should be showed as a range so I decided to use the histogram instead of a bar plot.
```{r}
gg<-ggplot(at,aes(x=MonthlyIncome))
gg<-gg+geom_histogram(binwidth = 1,fill="blue")
gg
``` 

#Create a graph that shows the average level of monthly income by field of education.
```{r}
MI_sum<-at%>%
  group_by(EducationField)%>% #each subsequenct command will be grouped by this
  summarize(income_avg=mean(MonthlyIncome)) #new variable = command

MI_sum
```

```{r}
gg<-ggplot(MI_sum,aes(x=EducationField,y=income_avg))
## Use bar plot geometry, height of bars set by level observed in dataset
gg<-gg+geom_bar(stat="Identity",fill="orange") #plot what's in the data set
## Print
gg
```


```{r}
## Same asethetics, but now orderred by level
gg<-ggplot(MI_sum,aes(x=fct_reorder(EducationField,income_avg),y=income_avg))

gg<-gg+geom_bar(stat="identity",fill="purple")

## Labeling
gg<-gg+xlab("Field of Education")+ylab("Average Income")
##Print
gg
```

#Create another graph that shows average level of monthly income by field of education and gender.
```{r}
## PLot it using a bar plot
gg<-ggplot(MI_sum,aes(x=fct_reorder(EducationField,attr_avg),y=attr_avg,color=Gender))
gg<-gg+geom_bar(stat="identity",aes(fill=Gender),position="dodge")
gg<-gg+ylab("Pr(Attrition)")+xlab("Frequency of Travel")
gg
```



```{r}
## Plot it using a dot plot
gg<-ggplot(MI_sum,aes(x=reorder(EducationField,attr_avg),y=attr_avg),color=Gender)
gg<-gg+geom_point(aes(color=Gender),size=5)
gg<-gg+coord_flip()
gg
```


#Create a graph that shows average levels of monthly income by field of education, gender and job level (scale of 1-5, highest ranked employees are 5)
```{r}
gg<-ggplot(MI_sum,aes(x=reorder(EducationField,attr_avg),
                      y=attr_avg,
                      fill=Gender))
## Bar plot, with unstacked (dodge)
 gg<-gg+geom_bar(stat="identity",position="dodge")
## Separate out by Job Level
gg<-gg+facet_wrap(~JobLevel)
## Change orientation to sideways
gg<-gg+coord_flip()
## Print
gg
```



